---
title: "DAES Practical Assignment"
author: "Azeez Olalekan, Baki"
date: "`r Sys.Date()`"
output:
  html_document: default
  pdf_document: default
  word_document: default
editor_options:
  markdown:
    wrap: 72
---

## Solution to Data Analysis Assignment

# Setting working directory

```{r setup, include=FALSE}
getwd()

setwd("C:/Users/dell/Downloads/MER Course/DAES 2022")

getwd()
```

## Install Packages

1.  ggplot2
2.  dplyr
3.  hrhrthemes

```{r}
library(ggplot2)
library(dplyr)
library(readr)
library(ggpubr)
library(ggsci)
library(pastecs)
```

## Importing the SOMLIT Dataset

```{r}
somlit <- read.table("SOMLIT.txt", header = T)
head(somlit)
```

1.  What are the variables in the dataset?

```{r}
variables <- colnames(somlit)
variables

ncol(somlit)
```

2.  How many observations are there in the dataset?

```{r}
observations <- nrow(somlit)

observations
```

## Exercise 2 : Time series analysis of chlorophyll-a concentration CHLA

-   Compute the basic descriptive statistics of CHLA
-   Generate the histogram of the relative frequency of CHLA (see Fig1)
-   Generate the time series of CHLA (see Fig2)

```{r, echo=TRUE}
descriptive_stat_CHLA <- summary(somlit$CHLA)
descriptive_stat_CHLA

summary_CHLA <- data.frame(Statistics = round(stat.desc(somlit$CHLA),2))
summary_CHLA

histogram_CHLA <-hist(somlit$CHLA)

barplot(histogram_CHLA$density,
        main = "Relative Distribution of the Chlorophyl-a",
        xlab = expression(paste("CHLA (",mu,"g/L)")),
        ylab = "Relative frequency",
        names.arg = histogram_CHLA$mids,
        col = "purple")


somlit$Year <-as.Date(somlit$DATE, "%d/%m/%Y")

plot(somlit$Year, somlit$CHLA, 
     type = "b",
     main = "Time Series of CHLA",
     xlab = "Year",
     ylab = expression(paste("CHLA (",mu,"g/L)")),
     col = "blue")

```

## Exercise 3 : Analysis of seasonal variability of CHLA

-   Compute the mean and the standard deviation of CHLA per season
    (Spring, Summer, Autumn, Winter)

```{r}
CHLA_seasons <- somlit %>%
  group_by(Season) %>% 
  summarise(Avg_CHLA = round(mean(CHLA),3),
            Std_CHLA = round(sd(CHLA),3)) %>% 
  arrange(desc(Avg_CHLA))
CHLA_seasons
  
```

-   Display the basic descriptive statistics of CHLA per season (Fig3)

```{r, echo=TRUE}
box_CHLA <- ggplot(data = somlit, aes(x=reorder(Season, CHLA), 
                                      y= CHLA, 
                                      fill= reorder(Season, CHLA)))+
  geom_boxplot()+
  labs(title = "CHLA: Seasonal Distribution of Chlorophy a",
       subtitle = " The Four Seasons: Fall, Summer, Winter, Spring",
       x="Seasons",
       y="CHLA (micro-g/L)",
       caption = "Data: Somlit by Prof Lubac",
       fill = "Season") +
  theme_classic()+
  scale_fill_aaas()
box_CHLA
```

## Exercise 4 : Detection of spring anomalies

-   Standardize CHLA variable (subtract the mean and divide by the
    standard deviation)
-   Find the date associated with CHLA values higher than 2.

```{r}
somlit<- somlit %>% 
  mutate(Standardize_CHLA = (CHLA-mean(CHLA))/sd(CHLA))
standard_CHLA <-data.frame(somlit$Standardize_CHLA)
head(standard_CHLA)

CHLA_higher_than_2 <- somlit %>% filter(CHLA>2)
date_2<-data.frame(CHLA_higher_than_2$DATE)
head(date_2)
```

## Exercise 5 : Relationship between CHLA and SPM

-   Display the relationship between CHLA and SPM (Fig4)

```{r, echo=TRUE}
CHLA_SPM <- ggplot(somlit, aes(x= CHLA, y= SPM, color = Season))+
  geom_point()+
  labs(title = "Relationship between CHLA and SPM",
       x=expression(paste("CHLA (",mu,"g/L)")),
       y="SPM",
       caption = "Data: Somlit by Prof Lubac",
       fill = "Season") +
  theme_classic()+
  scale_fill_aaas()
  
CHLA_SPM
```

## Exercise 6: Reproduce the same plots

Basic statistical distribution Name of the distribution Name of the R
function Parameters Binomiale binom size, prob Normale norm mean, sd
Khi-square chisq df Student t df Fisher f df1, df2 For each of these
distributions, you have 4 functions : ddistname, pdistname, qdistname,
rdistname, to calcualte respectively the PDF, the cumulative
distribution function, the quantile function (gives the result x such as
F(X=x) = p) and to generate random outcomes.

```{r, echo=TRUE}
#Binomial
binomiale <- dbinom(x=(0:5), size = 5, prob = 0.5)

plot(binomiale, 
     xlim = c(0,20), 
     ylim = c(0,0.4), 
     col= "black", 
     pch = 15, 
     ylab = "", 
     xlab = "")
points(dbinom(x=(0:10), size = 10, prob = 0.5), 
       col = "red", pch = 16) 
points(dbinom(x=(0:20), size = 20, prob = 0.5), 
       col = "green", pch = 17)
legend("top")

pbinom(q=(0:5), size = 5, prob = 0.5)
qbinom(p=(0.95), size = 5, prob = 0.5)
rbinom(n=(0:5), size = 5, prob = 0.5)

#Normal-distribution
x <- seq(-4, 4, 0.1)
plot(x, dnorm(x, mean = 0, sd = 1), type = "l",
     ylim = c(0.0, 0.4), ylab = "", xlab = "", col = "black", lty=2, lwd=2)
lines(x, dnorm(x, mean = 0, sd = 1.1), col = "green", lty=2, lwd=2)
lines(x, dnorm(x, mean = 0, sd = 1.05), col = "blue", lty=4, lwd=2)
lines(x, dnorm(x, mean= 0, sd=1.2), col= "red", lty=1, lwd=2)

```

## Exercise 7 : Problem !

Packets of seeds of Zostera are commercially available. In a packet
there are 15 seeds and each seed gives at most a foot of Zostera.
Seagrasses have a probability of germination equal to 0.85.

6.1. What is the minimum number of packets that a PhD student must
purchase to obtain at least 200 Zostera foot with a probability greater
than or equal to 0.95?

6.2. The Phd student has 100 euros to purchase the seeds. A packet is
sold 4.50 euros. How many feet should he expect to get?

```{r}
#X- B{15, 0.85^ny} = 0.95

ny <- log(0.0034)/log(0.85)
ny #seeds

#6.1: 35seeds needed equivalent to 3 packets
#6.2: He should be expecting 330feet of Zostera


#6.1 Correction
qbinom(p=0.95, size= 200, 0.85)
plot(200:230, qbinom(0.95,200:230,0.85))
abline(h=200, v=225)

#6.2: 
fd <-dbinom(c(0:330), 330, 0.85)
plot(fd~c(0:330),xlim=c(240,300), ylim=c(0,0.08), type="p")
plot(cumsum(fd)~c(0:330),xlim=c(240,300), ylim=c(0,1), type="p")
```
