---
title: "Assistance on R Assignment"
author: "Azeez Olalekan Baki"
date: "`r Sys.Date()`"
output:
  word_document: default
  html_document: default
  pdf_document: default
editor_options: 
  markdown: 
    wrap: 72
---

## Question one

# Assessing the penguins data from palmerpenguins package.

In order to access the data, I installed the package palmerpenguins and
make it accessible by R using the following lines of codes.

```{r setup, include=TRUE}
#install.packages("palmerpenguins")
library(palmerpenguins)
```

To know what is in the package and view how the data looks like. I used
the following lines of code:

From the code, I observed that the data has 344 rows/response and 8
columns/variables. The data has 3 factor variables, Species, Island and
Sex while the other variables are numeric and integer. Also, Adelie,
Chinstrap and Gentoo were the three penguins species the data contain.

```{r}
penguins
str(penguins) #for the type of the data
dim(penguins) #for dimension of the data
```

## Data cleaning

Upon inspecting the data, I observed 'NA' values which will hinder some
analysis on the data. Also, it was noticed that the data is not in the
table or dataframe format. Therefore, I performed the following to clean
and structure the data which was then stored using assignment operator
into a dataset called penguins_data.

```{r, echo=TRUE}
penguins_na<- na.omit(penguins)
penguins_data <- data.frame(penguins_na)
head(penguins_data)
```

## Descriptive analysis on the penguins data

In order to get more details of the data, I performed simple
descriptive analysis on the data and displayed it graphically using
boxplot. The following codes were used for the descriptive.

```{r}
summary(penguins_data)
boxplot(bill_length_mm~species, data=penguins_data, 
        main="Penguins Bill length", 
        ylab = "Bill length (mm)", 
        xlab = "Species", 
        col="bisque")
boxplot(bill_depth_mm~species, data=penguins_data, 
        main="Penguins Bill depth", 
        ylab = "Bill depth (mm)", 
        xlab = "Species", 
        col="bisque")
boxplot(flipper_length_mm~species, data=penguins_data, 
        main="Penguins flipper length", 
        ylab = "Flipper length (mm)", 
        xlab = "Species", 
        col="bisque")
boxplot(body_mass_g~species, data=penguins_data, 
        main="Penguins Body mass", 
        ylab = "Body mass (g)", 
        xlab = "Species", 
        col="bisque")
```

# Result

The boxplot shows that in terms of bill length, Adelie has low
median/mean compared to the other two species while Gentoo species has
the highest mean values for flipper length and body mass. Outliers were
also present in the dataset but for study purposes, they were not
removed from the data.

## Body mass mean of the penguins

Since the Gentoo shows high value for body mass among the species, there
is a need to have a look at the mean of each species. To do this, I
performed means by grouping using the inbuilt base r function "tapply"

```{r}
mean_body_mass<-tapply(penguins_data$body_mass_g, penguins_data$species, mean) 
mean_body_mass
```

# Result

Adelie Chinstrap Gentoo (3706.164 3733.088 5092.437). The result shows high
mean value for Gentoo (5092.437). The question that arises from this
figure is, does the mean value significant from the others?

## Significance of the body mass

To determine if the mean body mass is significant among the species, I
sorted the body mass data in terms of species and performed the
following assumptions: 1. Check of independence of variables 2. Test of
normality using Shapiro. This is done to determine if the data is from
normal distribution. 3. Choice of statistics. Since we are comparing
quantitative with qualitative data, we are in the realm of test of
hypothesis with large numbers.

#Hypothesis H0: No significant different among the means Ha: Atleasat
one of the means is different

# Separating the data

```{r}
attach(penguins_data) #To make r recognises that I will be working only with this data at the moment
X<-penguins_data[species=="Adelie",6] # Extracting the Adelie body mass
Y<-penguins_data[species=="Chinstrap",6] # Extracting the Chinstrap body mass
Z<-penguins_data[species=="Gentoo",6] # Extracting the Gentoo body mass
```

## Normality test using Shapiro

```{r}
shapiro.test(X)
shapiro.test(Y)
shapiro.test(Z)
```

# Result

The result shows that Adelie data is not normally distributed since the
p-value is less than 0.05 while the other two are normally distributed.
Since one of the data is not normally distributed, the non-parametric test can therefore be performed to determine the significance of the means.

Choice of Test: Kruskal-Wallis

```{r}
kruskal.test(body_mass_g~species, data = penguins_data)
pairwise.t.test(x=body_mass_g, g=species, data=penguins_data, p.adjust.method = "none")
```

# Result

The result shows that we reject the null hypothesis that there is no
significant different among the means. In other words, one mean is
significantly different from another p\<\<0.05. pairwise.t.test was
performed to know where the different lies. It was observed that Adelie
and Chinstrap body mass are not significant from each other (p\>0.05).
However, Gentoo species has mean value significantly higher than the
other two species (p\<\<0.05).

## Question two

Data to be used for this question was gotten from the modules in the 12
week tab. The data is on shrimps sampled from different families and
locations.

To load this csv data, "readr" package was installed and called using
the library function

```{r}
#install.packages("readr")
library(readr)
```

The data was then imported using the following code, in which the data
is called shrimp.

```{r}
shrimp <- read.csv("dorsal_spot_data (1).csv", header = TRUE) 
# header=TRUE, is to make r knows that our data has variable names as first row.
```

To assess the data, I used the following codes to view, look the
structure of the data and the dimension of the data.

```{r}
head(shrimp)
str(shrimp)
dim(shrimp)
```

Na's were also present in the data and will be removed by using na.omit
and the data will be saved in shrimp.

```{r}
shrimp <- na.omit(shrimp)
str(shrimp)
dim(shrimp)
```

Now, the NA's have been removed. From the data, we have character,
numeric and integer variables. The data has 20 rows and 16 variables.

## Descriptive statistics

```{r}
summary(shrimp)
plot(shrimp)
```

# Result

The summary function gives the simple descriptive of the variables in
the data. The plot functions therein shows different scatterplot among
the numerical and integer variables. Some of the variables have
relationship among each other while some do not. To view the correlation
better, I conducted a correlation analysis and graphically showed the
result using the corrplot package. First, I will install the package

```{r}
#install.packages("corrplot")
library(corrplot)
```

Since we are to use only independent variables with continuous data, I
would extract only the continuous variables and save it in data named
shrimp_1 using the following code.

```{r}
shrimp_1 <- shrimp[,-c(1:3,7,10,12,13)] 
#The code means I want all the rows and removed column, 1 to 3, 7, 10,12 and 13. 
#So, I will be left with the continuous data. To view the data in shrimp_1, I used the function view
head(shrimp_1)
```

Then I can conduct the correlation analysis. 
\## Correlation \#
Hypothesis H0: No relationship among the variables 
Ha: There is a  relationship

# Assumption

Test the conditions of application: - Independence of variables: YES -
Normality, using Shapiro

```{r}
shapiro.test(shrimp_1$rostc) #The dollar sign is to assess the variables in the data
shapiro.test(shrimp_1$rost)
shapiro.test(shrimp_1$cl)
```

# Result

Since some of the data is not normally distributed i.e p\<0.05 for
instance the rostc variable, we are to use the spearman correlation
method.

```{r}
corr <- cor(shrimp_1, method = "spearman")
corr
```

## Graphically

```{r}
corrplot(corr, method = "number", type = "lower", 
         main= "Correlation among the shrimp parameters")

#To check the significance of the correlation
cor.test(shrimp_1$cl, shrimp_1$depthn, method="spearman")
cor.test(shrimp_1$cl, shrimp_1$comno, method="spearman")
```

# Result

From the figure, It can be observed that cl has relationship with
depthn, depthm and comno. it can be noted from the data that depthn and
depthm are same data. It was observed that the relationship is not
significant.

## Influence of variables on size of shrimp species cl

To determine the influence of all the continous variables on cl, I
performed a simple linear regression (lm) using all the variables by
using "." to mean all the variables. I used the function summary to view
what is my model.

```{r}
model <- lm(cl~., data = shrimp_1)
summary(model)
```

# Result

The coefficient output shows the intercept, slopes for each variables
and significant level. The significant level shows that depth and depthn
are the two significant variables that can influence the shrimp size at
significant level of 0 '\***' and 0.001 '**'. We can therefore moderate
the model to include only the significant variables.

```{r}
model_1<- lm(cl~depth+depthn, data = shrimp_1)
summary(model_1)
```

# Result

It can be observed that at the absence of all other factors, depthn has
no significant effect while depth has significant effect at 0.1 alpha
level. The R-squared values shows that 57% of the response variable i.e
size of shrimp can be predicted from the variables. In other words, 57%
of the variation in the data was taken into account for the prediction
of the cl response. The p-value shows value less than alpha value of
0.05, indicating significant response of cl from depth and depthn. The
regression model can be computed as follow:

cl = 0.02320depth + 6.40509 cl = -1.01218depthn + 6.40509

# Model plot

```{r}
plot(model_1)
```

# Conclusion

From the result, we can say that the size of shrimp species depend to on
the depth at which the species is found. Invariably, shrimps found at
deeper depth has more size than those found at the surface of the
sediment.

## Question Three

Data to be used for this question was gotten from the modules in the 12
week tab. The data is on four crustacean species sampled from four
different size for four years. First, I load the data to access what is
in the data.

```{r}
crustacean <- read.csv("crustacean data.csv", header = TRUE)
head(crustacean)
```

## Research Questions

1.  is there a significant different in terms of size among the three
    crustacean species?.
2.  is the size also different among the sex?
3.  is there a relationship between the grade of the species and size?
4.  relationship between species and grade?

## Descriptive analysis

```{r}
summary(crustacean)
plot(density(crustacean$Size), type = "l", col="blue", main = "Distribution of the crustacean size", ylab = "Probability", xlab = "size")
boxplot(Size~Species, data = crustacean, col="bisque",  main = "Distribution of the crustacean size by species", ylab = "Size (mm)", xlab = "Species")
boxplot(Size~Grade, data = crustacean, col="bisque", main = "Distribution of the crustacean size by Grades", ylab = "Size (mm)", xlab = "Species")
size_spp<-tapply(crustacean$Size, crustacean$Species, mean); size_spp
size_spp_sd<-tapply(crustacean$Size, crustacean$Species, sd); size_spp_sd
size_sex<-tapply(crustacean$Size, crustacean$Sex, mean); size_sex
size_sex_sd<-tapply(crustacean$Size, crustacean$Sex, sd); size_sex_sd
barplot(size_sex, col = "bisque", ylab = "Mean value (mm)", xlab="Sex")
```

## Statistical test

is there a significant different in terms of size among the three
crustacean species?

Assumptions: 1. Check of independence of variables 2. Test of normality
using Shapiro. This is done to determine if the data is from normal
distribution. 3. Choice of statistics. Since we are comparing
quantitative with qualitative data, we are in the realm of test of
hypothesis with large numbers.

#Hypothesis H0: No significant different among the means Ha: Atleasat
one of the means is different

# Separating the data

```{r}
attach(crustacean) #To make r recognises that I will be working only with this data at the moment
A<-crustacean[Species=="Crab",8]# Extracting the crab 
B<-crustacean[Species=="Lobster",8] # Extracting the Lobster 
C<-crustacean[Species=="Velvet",8] # Extracting the Velvet
```

## Normality test using Shapiro

This test will not be useful since the data is large enough and any
small deviation will be significant. Therefore, we assume the data is
normally distributed.

## Homogeneity of variance/Homoscedasticity

```{r}
bartlett.test(Size~Species, data = crustacean)
```

# Result

The H0 is rejected the variance is not equal between the species.
Therefore, we are to perform non-parametric test

```{r}
kruskal.test(Size~Species, data = crustacean)
pairwise.t.test(x=Size, g=Species, data=crustacean, p.adjust.method = "none")
```

# Result

The H0 is rejected because p\<\<0.05. Therefore, the size of the
crustacean are significantly different from each other. Since the sizes
differ the question can be what can cause the different?

## Two way Anova and linear model

In order to determine the factors responsible for the different in size
among the species, Two way Anova was conducted. Simple linear model was
then used to show variables that can predict the size.

```{r}
Anova2 <-aov(Size~Species*Site*Sex, data = crustacean)
summary(Anova2)

mod <- lm(Size~Species+Site+Sex, data = crustacean)
summary(mod)
```

# Result

The result shows that the size of the species are significantly
different from each other in terms of all the variable individually and
in combination at except sex at 0.01 alpha value. Meanwhile, the linear
model shows that the species type and the site of samples have
significant impact on the size of the crustacean p\<\<0.05, with 73%
coefficient of determination.

## relationship between species and grade?

Formulation of hypotheses: - Ho: no relationship between the 2
qualitative variables. - Ha: relationship between the 2 qualitative
variables. Choice of the test: - chi-square test (test on the
contingency table). - The Fisher's exact test. Condition to use the
chi-square test: N larger than 50.

```{r}
tab<-table(Grade,Species);plot(tab)
chisq.test(tab)
```

# Result

The test returns the p-value which represents the probability to wrongly
reject Ho. Ho is rejected when p\<0.05. In this case, Ho is rejected
There is significant relationship between the 2 variables for a type I
error of 5%.

## Conclusion

From the analysis, we can say the size of crustacean depends on several
factors and the species of the crustacean.
