---
title: "Health Disease Prediction"
author: "Azeez O. Baki"
date: "25/12/2021"
output: word_document
---
## Setting Working Directory, Importing tidyverse library and Loading Data
```{r setup, include=FALSE}
getwd()
setwd("~/R")
library(tidyverse)
data <- read.csv("heart.csv")
head(data)
```

## Exploring the Data
```{r}
glimpse(data)
str(data)
```

## Checking for Missing values
```{r}
sum(is.na(data))
sum(is.null(data))
```
## Number of Rows and columns
```{r}
nrow(data)
ncol(data)
colnames(data)
```
## Summary of the Data
```{r}
summary(data)
```

## Data Transformation
This is done for easy visualization of the data when needed. Although, it is not necessary to do.
```{r}
data2 <- data %>% 
  mutate(sex = if_else(sex==1, "male", "female"),
         fbs = if_else(fbs==1, ">120", "<=120"),
         exang = if_else(exang==1,"yes", "no"),
         cp = if_else(cp==1,"Atypical Angina",
                      if_else(cp==2,"Non-Anginal pain", "Asymptomatic")),
         restecg = if_else(restecg==0,"Normal",
                           if_else(restecg==1, "Abnormality", "Probable or Definite")),
         slope = as.factor(slope),
         ca = as.factor(ca),
         thal =as.factor(thal),
         target = if_else(target== 1, "Yes", "No")
  ) %>% 
  mutate_if(is.character,as.factor) %>% 
  dplyr::select(target, sex, fbs, exang, cp, restecg, slope, ca, thal, everything())
```

## Data Visualization
To check what is going on with the data. we will be using ggplot to plot bar chart
```{r}
ggplot(data2, aes(x=target, fill=target))+
  geom_bar()+
  xlab("Heart Disease")+
  ylab("count")+
  ggtitle("Presence and Absence of Heart Disease")+
  scale_fill_discrete(name = "Heart Disease", labels = c("Absence", "Presence"))

```
 
 Since the plot above shows high number of people with heart disease, we can check the proportions.
```{r}
prop.table(table(data2$target))
```
 
## Comparing blood pressure across the chest pain
```{r}
data2 %>% 
  ggplot(aes(x=sex, y=trestbps))+
  geom_boxplot(fill = "purple")+
  xlab("sex")+
  ylab("BP")+
  facet_grid(~cp)
```
```{r}
data2 %>% 
  ggplot(aes(x=sex, y=chol))+
  geom_boxplot(fill = "yellow")+
  xlab("sex")+
  ylab("Chol")+
  facet_grid(~cp)
```

## Correlation
```{r}
library(corrplot)
cor_heart = cor(data2[, 10:14], method = "pearson")
cor_heart
corrplot(cor_heart, method= "ellipse", type = "full")
```
## Building Model

```{r}
library(caret)
heart_tr = trainControl(method = "repeatedcv", number = 10, repeats = 5)
model_rf = train(target~.,data2, method="rf", trControl = heart_tr)
model_rf
```

## To Predict the heart disease from the model using the data
```{r}
h_disease= predict(model_rf, data2) 
confusionMatrix(data2$target, h_disease)
```










