---
title: "Model"
author: "Azeez"
date: "24/12/2021"
output: word_document
---
## This workbook is to practice Machine Learning Algorithm using caret package.
The initial step is to call the library caret
```{r setup, include=FALSE}
library(caret)
```
## Dataset
Next is to load the data. The data to be used is iris dataset. Reason being that
the data has both numerical and categorical data to compute the supervised machine learning. 

```{r}
head(iris)
```
## Understanding the structure of the data
As data analyst, we need to check the structure of the data.
```{r, echo=FALSE}
str(iris)
class(iris)
```
## Data Exploration
This is done to get the trend and information to explore from the data. We do this 
through visualization,
```{r}
featurePlot(x=iris[,1:4],y=iris$Species, plot = "pairs")
```
Let use Box plot to show the distributions of the numerical data for the species.
```{r}
featurePlot(x=iris[,1:4], y=iris$Species, plot = "boxplot", auto.key = list(columns = 3), scale=list(y=list(relation="free")), labels=c('Species', 'length in cm'))
```
##Interpretation of the Visualisation
The result shows the distributions of the flower parts in all the three flowers.
It was observed that in petal.length, setosa flower has the low mean value while
virginica flower has high value of petal.length with high mean value. setosa and
versicolor have outliers.

## Scatter plot
Let check the relationship between the numerical data. To do this we use scatterplot.
```{r}
featurePlot(x=iris[,2:4],y=iris$Sepal.Length, plot = "scatter", labels=c("Other parts", "Sepal.Length"),scale=list(x=list(relation="free")))
```
## Observation
It was observed from the visualization that there is a relationship between the
all the flower parts. Sepal.length and petal.length shows promiscuous relationship.
To further shows this relationship we conduct correlation to determine the correlation
coefficient.

##Correlation
```{r}
cor_iris = cor(x=iris[,1:4], use = "everything", method = c("pearson"))
cor_iris
```
For proper understanding of the correlation result, we visualize it
## Correlation visualization
```{r}
#corrplot(cor_iris, method = "ellipse", type =c("full"))
```
We may like to check the summary of our flower parts.
```{r}
summary(iris[1:4])
summary(iris)
```

From the exploration of the data we see a trend and we can go ahead with our model.

##Algorithm
For our model, we will use trainControl with boot as the algorithm
```{r}
trc = trainControl(method = "boot", number = 25)
```

## Linear Regression model
```{r}
model_ft = train(Sepal.Length~.,iris, method="lm", trControl = trc)
model_ft
summary(model_ft)
```
```{r}
plot(model_ft$finalModel)
```
## Test model by predicting the train data from the model
```{r}
obs =predict(model_ft, iris)
#head(obs)
#head(iris)
plot(iris$Sepal.Length, obs)
abline(0,1)
plot(1:nrow(iris), iris$Sepal.Length)
points(1:nrow(iris),obs, col="red")
```

## Test model by predicting from new data 
We want to know the Sepal.Length with new value of other parts of the flower.
To do this, we new to create new dataset 
```{r}
new_data <- data.frame(Sepal.Width=c(1.7, 3.9, 4.0),
                       Petal.Length =c(1.0, 2.8, 7.1),
                       Petal.Width = c(0.4, 2.7, 3.2),
                       Species =c("setosa", "versicolor", "virginica"))
new_data
```

Now, we have the new data set, let predict the Sepal.Length from them
```{r}
obs = data.frame(Predicted_Sepal.Length=c(predict(model_ft, new_data)))
obs
```
## To model the flower from the flower part.
We are to perform classification, since our outcome is categorical
To do this we change our linear regression model to random forest.
```{r}
model_rf = train(Species~.,iris, method="rf", trControl = trc)
model_rf
```
##To predict the type of flower from the model

```{r}
flower_typ = predict(model_rf, iris)
confusionMatrix(iris$Species, flower_typ)
```
##To predict flower type from new data
```{r}
new_data <- data.frame(Sepal.Width=c(1.7, 3.9, 4.0),
                       Sepal.Length = c(5.0, 6.7, 9.0),
                       Petal.Length =c(1.0, 2.8, 7.1),
                       Petal.Width = c(0.4, 2.7, 3.2),
                       Species = c("setosa", "virginica", "virginica"))
obs <- data.frame(new_flower=c(predict(model_rf, new_data)))
obs
confusionMatrix(model_rf, new_data$species)
```






