---
title: "Real Data Work"
author: "Azeez"
date: "09/12/2021"
output:
  word_document: default
  pdf_document: default
---

Exercise using real data
  Topic: Nigerian Migration Survey

Research Questions
  #1 Do transnational migrants households earn higher income?
  #2 Are migrants more educated than non-migrants?
  #3 What is the effect of household religion on income?
  
Steps
  #1 checking working directory
  #2 upload the file

```{r, include=TRUE}
getwd()

library(haven)
consolidated <- read_dta("consolidated.dta")

library(haven)
individuals_5 <- read_dta("individuals 5.dta")

library(haven)
migrants_2 <- read_dta("migrants 2.dta")

library(haven)
non_hh_member_migrants_2 <- read_dta("non hh member migrants 2.dta")

```

## Checking variables names

```{r }
names(consolidated)
names(individuals_5)
names(migrants_2)
names(non_hh_member_migrants_2)
```

## Getting new file by combining the consolidated and individuals

```{r, echo=TRUE}
library(dplyr)

newdata <- left_join(consolidated, individuals_5, by = "record")
newdata

```
## Selection of only needed variables
```{r}
newdata1 <- newdata %>% select('record', 'ur',"religion", "maritalstatus", "age", "highestschooling", "food.x", "cookigfuel", 'clothigfootwear')
newdata1
```
## Calculating of mean
```{r}
newdata1$food.x <- as.numeric(as.double(newdata1$food.x))

mean(newdata1$food.x, na.rm=TRUE)
```
## Joining newdata1 with migrant
```{r}
newdata2 <- left_join(newdata1, migrants_2, by = "record")
newdata2
```
## adding new column in the data

  #note: In dplyr: select is used to extract variables
                  filter is used to extract rows
                  mutate is used to create new column/variable
```{r}
newdata3 <- newdata2 <- left_join(newdata1, migrants_2, by = "record") %>% 
  filter(ur==2) %>% 
  mutate(expendit = food.x + cookigfuel + clothigfootwear)
```
## Regression Analysis
    Note: when computing effect with two level (yes,no) use binomial i.e gm
          otherwise use lm (linear regression)
```{r}
regression1 <- lm(expendit ~ factor(religion)+ factor(maritalstatus), data=newdata3)
summary(regression1)
```
## Interpretation of the Regression result
    y=a+bx+c
The result make reference to one of the religion 1(Islam). Showing that religion2 is earning 1896 + 19782, religion3 earned 16863 more of religion1.

Conclusion Religion 3 and 4 are statistically significant from the other religions i.e they spent more.










